Supporting Information : Understanding the Nanoscale Structure of Inverted Hexagonal Phase Lyotropic Liquid Crystal Polymer Membranes

### 2018-10-05 Ben_Manuscripts/structure_paper/supporting_information.tex
Added links to code

\externaldocument[M-]{Draft}
\title{Supporting Information : Understanding the nanoscale structure of hexagonal phase lyotropic liquid crystal membranes}
\author{Benjamin J. Coscia \and Douglas L. Gin \and Richard D. Noble \and Joe Yelk \and Matthew Glaser \and Xunda Feng \and Michael R. Shirts}

>>>>

\externaldocument[M-]{Draft}
\title{Supporting Information : Understanding the Nanoscale Structure of Inverted Hexagonal Phase Lyotropic Liquid Crystal Polymer Membranes}
\author{Benjamin J. Coscia \and Jospeh Yelk \and Matthew A. Glaser \and Douglas L. Gin \and Xunda Feng \and Michael R. Shirts}
\date{}
